---
title: "Statistical Analysis"
output: html_notebook
---

Loading in packages:
```{r}
library(readr) 
library(ggplot2)
library(scales)
library(ggthemes)
library(tidyverse)
```

Loading in data:
```{r}
data <- read_csv("C:/Users/Kayla5SOS/Documents/mejo570/finalstory/data.csv")
head(data)
```

For my statistical analysis, I want to use regression to look at a country's vulnerability to climate change and the % of their GDP that comes from the Agriculture sector. My hypothesis is that these values aren't just very closely correlated, but that the % of a country's GDP that comes from agriculture is going to be a huge deciding factor in a country's vulnerability (this will be decided looking at the adjusted r-squared value).

```{r}
fit <- lm(`%GDP AG` ~ `2017 Vulnerability`, data = data)
summary(fit)
```

Analysis: 
My p-value of .0000000000000022 tells me that there is a very strong correlation/connection between a country's vulnerability and the percentage of their GDP that comes from agriculture, the correlation is definitely not random 
My adjusted r-squared value of .5831 tells me that 58.31% of a country's vulnerability score can be attributed to the % of their GDP that comes from agriculture. 

News Worthy Summary: 
According to data from the World Bank, there is a very strong correlation between the percentage of a country's GDP that comes from the agriculture industry and their vulnerability to climate change. In fact, over half of a country's vulnerability score can be solely determined by the percentage of their GDP that comes from agriculture. 









